\bf Approachable case studies support learning and reproducibility in data science: An example from evolutionary biology

### 2022-06-11 jsdse/latex_submission/Manuscript.tex
jsdse resubmission files

Using a case study within evolutionary biology, we identify aspects of research workflows that make them unapproachable to the general audience:
use of highly specialized language;
unclear goals and high cognitive load; and
lack of trouble-shooting examples.
We propose a set of principles to improve the unapproachable aspects of research workflows, and illustrate their application using an online teaching resource.
We elaborate on the general application of these principles for documenting not only research products but also teaching materials, to provide present learners and future researchers with tools for successful scientific reproducibility.
%> ** add a sentence on implications for teaching reproducibility

>>>>

Using a case study within evolutionary biology, we identify aspects of research workflows that make them unapproachable to the general audience:
use of highly specialized language;
unclear goals and high cognitive load; and
lack of trouble-shooting examples.
We propose principles to improve the unapproachable aspects of research workflows, and illustrate their application using an online teaching resource.
We elaborate on the general application of these principles for documenting research products and teaching materials, to provide present learners and future researchers with tools for successful scientific reproducibility.
%> ** add a sentence on implications for teaching reproducibility
